Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-07 paper/paper.tex
pass on V.B.

\begin{itemize}
  \item \textbf{Undefined Behavior.} False positives of this kind are
    manifested when tests cover implementation-dependent behavior, as
    defined in the ECMA262 specification~\cite{ecmas262-spec}. For
    example, one of the tests from \jerry\ uses the function
    \CodeIn{Number.toPrecision([precision])}, which translates a
    number to a string, considering a given number of significant
    digits. The floating-point approximation of the real value is
    implementation-dependent, making the test to pass only in
    \chakra\ for that test.

  \item \textbf{Timeout/OME\footnote{ome is for out of memory
      error.}.} False positives of this kind manifest when the target
    engine that runs the test do not optimize code as the original
    engine. For that, tests fail to finish at the time budget or runs
    out of memory.\Comment{For example, we found that only \jsc{} implements
    tail-call optimization to avoid tail recursion.}\Mar{concrete example!}

  \item \textbf{Not implemented.} False positives of this kind
    manifest when a test fails because it covers a function that is
    part of the official spec, but is not implemented in the target
    engine. For example, at the time of writing, Chakra does not
    implement various properties from the \mcodeid{Symbol} object.

  \item \textbf{Unknown.} This source corresponds to the cases we were
    unable to confidently diagnose the failure.

@@

\begin{table*}[t]
  \vspace{-3ex}
%  \scriptsize
  \centering
  \caption{List of bug reports issued as result of test transplantation.}
  \label{tab:test-transplantation-bugs}
  \begin{tabular}{cccccccc}
    \toprule Issue\#    & Date & Fuzz & Engine  & Status  & \multicolumn{1}{c}{Url}  & Severity & Suite \\
    \midrule    
    1  & 4/18 & \crossmark & JavascriptCore  & New  & \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749}} & \Fix{x} & JerryScript      \\
   2  & 4/23 & \crossmark & Chakra  & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5033}{\#5033}} & \Fix{x} & Mozilla      \\
   3  & 4/29 & \crossmark & Chakra  & \textbf{Confirmed}   &
    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5065}{\#5065}} & \Fix{x} & Mozilla \\
   \multirow{2}{*}{4}  & \multirow{2}{*}{4/29} &  \multirow{2}{*}{\crossmark} & Chakra & \textbf{Confirmed} &    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5067}{\#5067}} & \multirow{2}{*}{\Fix{x}} & \multirow{2}{*}{Mozilla}\\
                       &  &                       &
    JavascriptCore & New &    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185130}{\#185130} } &   & \\
   5 & 5/02 & \crossmark & JavascriptCore & New  & \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208}} & \Fix{x} & Mozilla \\
   6 & 5/17 & \crossmark & Chakra & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5187}{\#5187}} & \Fix{x} & \jsc{}\\
   7 & 5/21 & \crossmark & Chakra & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5203}{\#5203}} & \Fix{x} & Mozilla\\
   8 & 6/28 & \crossmark & Chakra & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5388}{\#5388}} & \Fix{x} & \jsc{}\\
   9 & 7/10 & \crossmark & Chakra & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5442}{\#5442}} & \Fix{x} & JerryScript\\
   10 & 7/18 & \crossmark & Chakra & \textbf{Fixed} & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5478}{\#5478}} & \Fix{x} & Mozilla\\
   11 & 7/18 & \crossmark & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187777}{\#187777}} & \Fix{x} & JerryScript\\
   12 & 8/07 & \crossmark & Chakra & New & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5576}{\#5576}} & \Fix{x} & JerryScript\\
   13 & 8/07 & \crossmark & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188378}{\#188378}} & \Fix{x} & JerryScript\\
   \bottomrule
  \end{tabular}
\end{table*}

>>>>

\begin{itemize}
  \item \textbf{Undefined Behavior.} False positives of this kind are
    manifested when tests cover implementation-dependent behavior, as
    defined in the ECMA262 specification~\cite{ecmas262-spec}. For
    example, one of the tests from \jerry\ uses the function
    \CodeIn{Number.toPrecision([precision])}, which translates a
    number to a string, considering a given number of significant
    digits. The floating-point approximation of the real value is
    implementation-dependent, making the test to pass only in
    \chakra\ for that test. \Igor{ Several tests explores 
    the error message from a function violation, due the error
    message string is distinct and the type of Error is equal,
    we considered these cases as undefined behavior too.
    }

  \item \textbf{Timeout/OME\footnote{ome is for out of memory
      error.}.} False positives of this kind manifest when the target
    engine that runs the test do not optimize code as the original
    engine. For that, tests fail to finish at the time budget or runs
    out of memory.\Comment{For example, we found that only \jsc{} implements
    tail-call optimization to avoid tail recursion.}
    \Igor{
      For example, a testcase from \jsc{} suite explores the tail call
      to optimize the recursion, the test uses a recursive function that
      should be executed multiple times (ie. \mcodeid{1e6}). In this case, 
      only the \jsc{} supports tail-call optimization and the testcase 
      passes without failures. Another case can be found in JerryScript suite
      that uses a repetition statement to concatenate long strings 
      exponentially, causing an out of memory error. The engines used 
      supports the flags to increase memory, however we prefer to use 
      the default engine build.
    }

  \item \textbf{Not implemented.} False positives of this kind
    manifest when a test fails because it covers a function that is
    part of the official spec, but is not implemented in the target
    engine. For example, at the time of writing, Chakra does not
    implement various properties from the \mcodeid{Symbol} object, 
    \Igor{these implementation are in experimental mode 
    (ie. activating with flag -ES6Experimental)}.

  \item \textbf{Unknown.} This source corresponds to the cases we were
    unable to confidently diagnose the failure.
    \Igor{
      We observed that some tests are not valid due
      not corresponds to the ES6 specifications,
      we skip these warnings.
    }

@@

\begin{table*}[t]
  \vspace{-3ex}
%  \scriptsize
  \centering
  \caption{List of bug reports issued as result of test transplantation.}
  \label{tab:test-transplantation-bugs}
  \begin{tabular}{cccccccc}
    \toprule Issue\#    & Date & Fuzz & Engine  & Status  & \multicolumn{1}{c}{Url}  & Severity & Suite \\
    \midrule    
    1  & 4/18 & \crossmark & JavascriptCore  & New  & \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749}} & \Fix{x} & JerryScript      \\
   2  & 4/23 & \crossmark & Chakra  & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5033}{\#5033}} & \Fix{x} & Mozilla      \\
   3  & 4/29 & \crossmark & Chakra  & \textbf{Confirmed}   &
    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5065}{\#5065}} & \Fix{x} & Mozilla \\
   \multirow{2}{*}{4}  & \multirow{2}{*}{4/29} &  \multirow{2}{*}{\crossmark} & Chakra & \textbf{Confirmed} &    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5067}{\#5067}} & \multirow{2}{*}{\Fix{x}} & \multirow{2}{*}{Mozilla}\\
                       &  &                       &
    JavascriptCore & New &    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185130}{\#185130} } &   & \\
   5 & 5/02 & \crossmark & JavascriptCore & New  & \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208}} & \Fix{x} & Mozilla \\
   6 & 5/17 & \crossmark & Chakra & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5187}{\#5187}} & \Fix{x} & \jsc{}\\
   7 & 5/21 & \crossmark & Chakra & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5203}{\#5203}} & \Fix{x} & Mozilla\\
   8 & 6/28 & \crossmark & Chakra & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5388}{\#5388}} & \Fix{x} & \jsc{}\\
   9 & 7/10 & \crossmark & Chakra & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5442}{\#5442}} & \Fix{x} & JerryScript\\
   10 & 7/18 & \crossmark & Chakra & \textbf{Fixed} & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5478}{\#5478}} & \Fix{x} & Mozilla\\
   11 & 7/18 & \crossmark & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187777}{\#187777}} & \Fix{x} & JerryScript\\
   12 & 8/07 & \crossmark & Chakra & New & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5576}{\#5576}} & \Fix{x} & JerryScript\\
   13 & 8/07 & \crossmark & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188378}{\#188378}} & \Fix{x} & JerryScript\\
   14 & 8/07 & \crossmark & Chakra & New & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5579}{\#5579}} & \Fix{x} & JerryScript\\
   15 & 8/07 & \crossmark & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188382}{\#188382}} & \Fix{x} & JerryScript\\
   \bottomrule
  \end{tabular}
\end{table*}
